---
title: '**DaSL Collection**'
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "Description about Course/Book."
favicon: assets/dasl_favicon.ico
always_allow_html: true
output:
    bookdown::html_document2:
      toc: true
---

# About this Collection

The following tables are rendered automatically from our resources using the GitHub API. 

## Courses

The following are our courses, indicated by the `course` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source("scripts/render_collection.R")
DT::datatable(
  make_collection_table(kable = FALSE, include = "course") # must include "course" tag from github
)
```

## Fred Hutch Learning

The following are materials specific to Fred Hutch Cancer Center, indicated by the `hutch-course` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
DT::datatable(
  make_collection_table(kable = FALSE, include = "hutch-course") # must include "hutch-course" tag from github
)
```

## EdTech Software

The following are tools and software we've designed to make training more streamlined and reproducible. They have the `edtech-software` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
DT::datatable(
  make_collection_table(kable = FALSE, include = "edtech-software") # must include "edtech-software" tag from github
)
```

