---
title: '**DaSL Collection**'
date: "`r format(Sys.time(), '%B, %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "Description about Course/Book."
favicon: assets/dasl_favicon.ico
always_allow_html: true
output:
    bookdown::html_document2:
      toc: true
---

# About this Collection

The following tables are rendered automatically from our resources using the GitHub API. 

## Courses

The following are our courses, indicated by the `course` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source("scripts/render_collection.R")

knitr::kable(make_collection_table(kable = TRUE, include = "course"), format = "html")

devtools::install_github('rstudio/DT')
update.packages(ask = FALSE, checkBuilt = TRUE)
library(DT)
datatable(head(iris, 20), options = list(
  initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({
      'background-color': '#000',
      'color': '#fff'
     });",
    "}")
))
```

## Fred Hutch Learning

The following are materials specific to Fred Hutch Cancer Center, indicated by the `hutch-course` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source("scripts/render_collection.R")

knitr::kable(make_collection_table(kable = TRUE, include = "hutch-course"), format = "html")
```

## EdTech Software

The following are tools and software we've designed to make training more streamlined and reproducible. They have the `edtech-software` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source("scripts/render_collection.R")

knitr::kable(make_collection_table(kable = TRUE, include = "edtech-software"), format = "html")
```

<br><br><br>
This page was last updated on `r Sys.time()`

