---
title: '**DaSL Collection**'
date: "`r format(Sys.time(), '%B, %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
description: "Description about Course/Book."
favicon: assets/dasl_favicon.ico
always_allow_html: true
output:
    bookdown::html_document2:
      toc: true
---

# About this Collection

The following tables are rendered automatically from our resources using the GitHub API. 

## Courses

The following are our courses, indicated by the `course` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source("scripts/render_collection.R")

knitr::kable(make_collection_table(kable = TRUE, include = "course"), format = "html")
```

```{r echo = FALSE}
library(DT)
dt_table <- iris %>% DT::datatable(
  rownames = FALSE,
  #caption = 'Table 1: This is a simple caption for the table.',
  class = 'cell-border stripe',
  escape = FALSE,
  filter = "top",
  extensions = list("Scroller"),
  #   options = list(autoWidth = FALSE,
  # columnDefs = list(width = '300px', width = '200px', width = '90px', width = '200px', width = '100px'),
  
  options = list(
    autoWidth = TRUE,
    columnDefs = list(
      list(
        targets = c(0),
        visible = TRUE,
        width = '120'
      ),
      list(
        targets = c(1),
        visible = TRUE,
        width = '120'
      ),
      list(
        targets = c(2),
        visible = TRUE,
        width = '110'
      ),
      list(targets = '_all', visible = FALSE)
    ),
    
    pageLength = 10,
    scrollY = TRUE,
    scrollX = TRUE,
    scrollCollapse = TRUE,
    fillContainer = TRUE,
    initComplete = JS(
      "function(settings, json) {",
      "$(this.api().table().header()).css({'background-color': '#888888', 'color': '#fff'});",
      "}"
    )
  )
)
  
 
```

``` {r echo = FALSE, include=TRUE}
dt_table
```

## Fred Hutch Learning

The following are materials specific to Fred Hutch Cancer Center, indicated by the `hutch-course` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source("scripts/render_collection.R")

knitr::kable(make_collection_table(kable = TRUE, include = "hutch-course"), format = "html")
```

## EdTech Software

The following are tools and software we've designed to make training more streamlined and reproducible. They have the `edtech-software` tag.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
source("scripts/render_collection.R")

knitr::kable(make_collection_table(kable = TRUE, include = "edtech-software"), format = "html")
```

<br><br><br>
This page was last updated on `r Sys.time()`

